---
title: "R Coding Exercise"
output:
  html_document:
    toc: FALSE
---

##Loading and checking data
```{r}
#load dslabs, dplyr, and ggplot2 packages
library(dslabs)
library(tidyverse)
```


```{r}
#look at help file for gapminder data
help(gapminder)
#get an overview of the structure of gapminder data
str(gapminder)
#get a summary of data
summary(gapminder)
#determine the type of object gapminder is
class(gapminder)
```
##Processing Data
```{r}
#filter gapminder data for only countries in the continent of Africa and assign to africadata
africadata <- filter(gapminder, continent=="Africa")
#verify structure and summary of africa data has correct number of observations
str(africadata)
summary(africadata)
```
```{r}
#create object with infant_mortality and life_expectancy out of africadata
infandlife <- africadata %>% select(infant_mortality, life_expectancy)
#create object with population and life expectancy out of africadata
popandlife <- africadata %>% select(population, life_expectancy)
#check structure and summary of both objects popandlife and infandlife
str(popandlife)
summary(popandlife)
str(infandlife)
summary(infandlife)
```
##Initial Plotting
```{r}
#create a scatterplot of infant_mortality and life_expectancy
ggplot(data=infandlife, aes(x=infant_mortality, y=life_expectancy))+geom_point()+
  xlab("Infant Mortality")+ylab("Life Expectancy")+labs(title="Infant Mortality vs. Life Expectancy")
```


```{r}
#create a scatterplot of population and life expectancy with population on the log scale
ggplot(data=popandlife, aes(x=log(population), y=life_expectancy))+ geom_point()+xlab("Population")+ylab("Life Expectancy")+labs(title="Population vs. Life Expectancy")
```
```{r}
#group the africadata by year and filter missing data on infant mortality by year
africadata %>% select(year, infant_mortality) %>% group_by(year) %>% filter(is.na(infant_mortality)) %>% count()
#create a new object filtering africadata for only the year 2000
africa2000 <- filter(africadata, year==2000)
#confirm new object africa2000 has correct number of observations
str(africa2000)
summary(africa2000)
```
```{r}
#create object with infant mortality and life expectancy from the year 2000
infandlife2 <- africadata %>% filter(year==2000) %>% select(infant_mortality, life_expectancy)
#create object with population and life expectancy from the year 2000
popandlife2 <- africadata %>% filter(year==2000) %>% select(population, life_expectancy)
```


```{r}
#create a scatterplot of infandlife2
ggplot(data=infandlife2, aes(x=infant_mortality, y=life_expectancy))+geom_point()+labs(title="Infant Mortality vs. Life Expectancy in 2000")+xlab("Infant Mortality")+ylab("Life Expectancy")
```
```{r}
#create a scatterplot of popandlife2
ggplot(data=popandlife2, aes(x=log(population), y=life_expectancy))+ geom_point()+xlab("Log Population")+ylab("Life Expectancy")+labs(title="Population vs. Life Expectancy in 2000")
```
##Fit
```{r}
#fit life expectancy and infant mortality
fit1<- lm(life_expectancy~infant_mortality, infandlife2)
#fit life expectancy and population
fit2<- lm(life_expectancy~population, popandlife2)
#call summary of fit1
summary(fit1)
#call summary of fit2
summary(fit2)
```
Infant mortality and life expectancy are significantly correlated at the 0.05 level but population and life expectancy are not.

# This section is added by Christian Okitondo

## Let's create a plot assessing the relationship between life expectancy and mortality in 2000 and look at the impacted region
```{r}
ggplot(africa2000, aes(x=infant_mortality, y=life_expectancy, color=region)) +geom_point()
```


## Let's run another regression prediction the average life expectancy in each region
```{r}
fit3 <- lm(life_expectancy ~ region, data = africa2000)
summary(fit3)
```

This shows that there was a significance difference in life expectancy in the Northern Africa region.

