This data is from the CDC website at https://data.cdc.gov/Foodborne-Waterborne-and-Related-Diseases/Botulism/66i6-hisz
and has counts of confirmed botulism cases in the United States by state, year, type of botulism toxin, and transmission type. I will be cleaning an working with all 5 variables.
```{r}
#load tidyverse
library(tidyverse)
#read in the data and assign to botulismdata
botulismdata<-read_csv("dataanalysis-exercise/rawdata/Botulism.csv")
#checking structure and summary of data set
str(botulismdata)
summary(botulismdata)
```
BotType and ToxinType are both classified as characters but would be better represented as factors so I will change them.

```{r}
#change BotType and ToxinType to factor variables
botulismdata$BotType <- as.factor(botulismdata$BotType)
botulismdata$ToxinType <- as.factor(botulismdata$ToxinType)
#confirm they were both changed
str(botulismdata)
```
Next, I think the BotType and ToxinType variables can be renamed to be a little clearer.
```{r}
#Rename the BotType and ToxinType variables
botulismdata <- rename(botulismdata, "Transmission Type" = "BotType")
botulismdata <- rename(botulismdata, "Toxin Type" = "ToxinType")
#Confirm the names changed correctly
str(botulismdata)
```
```{r}
#Check is there is any missing data
colSums(is.na(botulismdata))
```
All the NA entries appear to be in the state column. There are 2280 observations so I decided to just remove the 34 NA values since they don't make up a large percentage of the data overall.
```{r}
#Drop the NA values in the state column
botulismdata <- drop_na(botulismdata, State)
#Confirm number of observations dropped from 2280 to 2246
str(botulismdata)
```
```{r}
##install and load psych package to use describe to see a summary of data, also run summary
install.packages("psych")
library(psych)
summary(botulismdata)
describe(botulismdata)
```
Save as RDS file
```{r}
saveRDS(botulismdata, file="cleanbotulismdata")
```

