---
title: "Flu Analysis Exploration"
output:
  html_document:
    toc: FALSE
---

## Load Packages

```{r}
#load in necessary packages
library(tidyverse)
```

## Load Clean Data

```{r}
#load in the cleaned data
flurevise<- readRDS(file = "../data/flurevised.rds")
flurevise
```


```{r}
#get a summary of the variables
flurevise %>% select(BodyTemp, Nausea) %>% summary()
```

## Data Exploration 

```{r}
#create a histogram of the continuous variable BodyTemp 
ggplot(flurevise, aes(x=BodyTemp))+geom_histogram()+labs(title="Body Temperature Frequencies", x="Body Temperature", y="Count")+theme_bw()
```
The distribution looks fairly normal with most of the temps at normal human ranges from around 98-99 degrees, with nothing looking implausible. There are a few across the 100-103 range which could be considered indicative of a fever.

```{r}
ggplot(flurevise, aes(x=Nausea, y=BodyTemp, fill=Nausea))+geom_boxplot()
```
Here I was checking how the two outcomes of interest compared to each other in a box plot, they have a pretty even body temperature distribution between those that reported nausea and those that didn't. 


```{r}
ggplot(flurevise, aes(x=SwollenLymphNodes, y=BodyTemp, fill=SwollenLymphNodes))+geom_boxplot()+labs(title = "Body Temperature Distribution by Lymph Node Status", x="Swollen Lymph Nodes", y="Body Temperature")
```
It seems from a glance that body temperatures were slightly higher in people who reported no swollen lymph nodes.

```{r}
ggplot(flurevise, aes(x=CoughIntensity, y=BodyTemp, fill=CoughIntensity))+geom_boxplot()+labs(x="Cough Intensity", y="Body Temperature", title="Body Temperature Distribution by Cough Intensity")
```
Body temperature tended to trend higher with more intense coughing.

```{r}
ggplot(flurevise, aes(x=RunnyNose, y=BodyTemp, fill=RunnyNose))+geom_boxplot()+labs(title="Body Temperature Distribution by Presence of Runny Nose", x="Runny Nose Status", y="Body Temperature")
```

