---
title: "Fitting Flu Analysis"
output:
  html_document:
    toc: FALSE
---
## Load Packages
```{r}
library(tidyverse)
library(tidymodels)
library(performance)
```


## Load Data
```{r}
#loading cleaned data
flufinal<- readRDS(file = "../data/flurevised.rds")
```

## Fitting
First I am going to run a linear regression using the main predictor of interest, RunnyNose, against the main continuous outcome of interest, BodyTemp.
 
```{r}
lm_mod <- linear_reg() %>% set_engine("lm")
fitlm1 <- lm_mod %>%
  fit(BodyTemp ~ RunnyNose, data=flufinal)
#checking results
fitlm1
tidy(fitlm1)
glance(fitlm1)
```
From this regression it seems that having a runny nose was negatively correlated with body temperature.

Next we'll do another linear model with Body Temperature as the outcome but include all the predictors in the data set.
```{r}
fitlm2 <- lm_mod %>% fit(BodyTemp~., data=flufinal)
#checking results
tidy(fitlm2)
glance(fitlm2)
```

Now we will compare th performance of the two models.
```{r}
compare_performance(fitlm1, fitlm2)
```
According to the R2 value, the second fit with all of the predictors included was better than the first fit with only RunnyNose as a predictor.


Next we'll take a look at our other outcome of interest, Nausea. We'll run a logistic regression with RunnyNose as the predictor.
```{r}
glm_mod <- logistic_reg() %>% set_engine("glm")
fluglm1 <- glm_mod %>% fit(Nausea ~ RunnyNose, data=flufinal)
#checking results
tidy(fluglm1)
glance(fluglm1)
```

Then we'll run another logistic regression with all the predictors of the data and nausea still as the outcome.
```{r}
fluglm2<- glm_mod %>% fit(Nausea ~., data=flufinal)
#checking results
tidy(fluglm2)
glance(fluglm2)
```

Then we'll compare the performance of the two logistic models.
```{r}
compare_performance(fluglm1, fluglm2)
```

The global model seems to be a better predictor of nausea than just the presence or absence of a runny nose.